An introduction to lightlabsFDS

### 2012-02-29 presentations/lightlabsFDS_mar-2012/pres.tex
Updated presentation.

\BIT
\I  Frequency-domain solver made possible by correct choice of PML and 
        linear algebra algorithm.
\I  See: Wonseok Shin, Shanhui Fan, 
            ``Choice of the perfectly matched layer boundary condition for 
            frequency-domain Maxwell's equations solvers'',
            Journal of Computational Physics (January 2012).
\EIT

\oursection{Interface}
\BIT
\I  No installation required.
\begin{verbatim}
>>> [E, H] = fds(omega, epsilon, J); % Run FDS.
\end{verbatim}
\EIT
\end{document}

>>>>

Picture from paper here.
\BIT
\I  Frequency-domain solver made possible by correct choice of PML and 
        linear algebra algorithm.
\I  See: Wonseok Shin, Shanhui Fan, 
            ``Choice of the perfectly matched layer boundary condition for 
            frequency-domain Maxwell's equations solvers'',
            Journal of Computational Physics (January 2012).
\EIT

\oursection{Interface}
\textbf{We want engineers and scientists to absolutely love using FDS
        and, at the same time, to forget about it because it just works.}
\BIT
\I  No installation, just start up Matlab and
\begin{verbatim}
>>> [E, H] = fds(omega, epsilon, J); % Done.
\end{verbatim}
\I  Helper functions to
    \BIT
    \I  construct the optical structures $(\epsilon, \mu)$,
    \I  define the input excitations $(J)$, and
    \I  analyze and visualize the output fields $(E,H,D,B)$
    \EIT
    are all included and open-sourced.
\I  Additionally, lots of examples and tutorials.
\EIT

\oursection{Hardware}
Hub and spokes picture here.
\BIT
\I  Centralized, shared, custom-tuned server able to deliver the performance
        of a large cluster
\I  Performance achieved via heavily optimized GPU code
\I  Multiple servers can be clustered with nearly $100\%$ computational
        efficiency.
\EIT

\oursection{Current status}
\BIT
\I  Algorithm: Implemented on GPUs, still optimizing (Jesse)
\I  Interface: (Wonseok)
\I  Hardware: Prototype ordered and being built (Jesse)
\EIT
\end{document}
